\tiny \begin{longtable} { |p{0.22\textwidth}  |r  |r |} 
\caption{Overhead costs per rack \label{tab:overheads}}\\ 
\hline 
\textbf{Item}&\textbf{Number/ Cost} \\ \hline
{Compute nodes in a rack }&{36} \\ \hline
{Rack initial cost has power, networking switches, networking cables, ready for machine installation-- switches last 5 years.  Will need to refresh, but rack should last entire project.  }&{\$24,000.00} \\ \hline
{ ** need to add annually: floor space for rack for 1 years.   need to renew after new nodes are racked/ stacked }&{\$300} \\ \hline
{** Need to add annually: power for 1 node for 1 yr - kw * rate * hours/ year * }&{\$348} \\ \hline
{** need to add annually: cooling for 1 node for 5 years  kw* chilled water per MBTU* hours/ year *  1KW in (MBTU) }&{\$210} \\ \hline
{** Need to add annually: maintenance for nodes -- can't purchase more than what the contract has in time left.  could be included in the price of the machine, and might not be added in here.  }&{\$1,500} \\ \hline
{Cost for each machine for 1 year in a rack.   }&{\$566} \\ \hline
{**** need to add in at an annual basis.  software maintenance (oracle and other software not associated with specific node annually)  Oracle license, VM licensing.  }&{\$35,000} \\ \hline
{Power per Rack (for Chile) Watts}&{12096} \\ \hline
{Approx PB per Storage Rack }&{8} \\ \hline
{Compute node lifetime (years)}&{3} \\ \hline
{Storage lifetime (years)}&{5} \\ \hline
{Chile Power CLP /  KW-hr
}&{105.65} \\ \hline
\end{longtable} \normalsize
